demographicvariablesregression

### 2023-02-09 combined data set/demographicvariables.Rmd
non parametric tests added for gender

@@

caste_gender2 %>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")

>>>>

```{r}
#checking distribution of age

library(ggplot2)

ggplot(joineddf, aes(x = age)) +
  geom_bar(fill = "blue", alpha = 0.5) +
  labs(x = "Age", y = "Frequency") +
  ggtitle("Distribution of Age")

@@

caste_gender2 %>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived benefit", y = "GenderXCaste groups")

### 2023-02-09 combined data set/demovariablesregression.Rmd
non parametric tests added for gender

---
title: "distributions"
output:
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
  pdf_document:

@@

@@

#Urban population

```{r, echo =FALSE}
#Distribution checks 
joineddf %>%
  filter(urban_rural == "Urban") %>%
  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
  geom_bar(fill = "firebrick2")+
  labs(x= "Perceived Risk from Nuclear Energy", y = "Urban population")
```

```{r, echo =FALSE}

joineddf %>%
  filter(urban_rural == "Urban") %>%
  ggplot(aes(x=Risky_Hydro, y = ..count..))+
  geom_bar(fill = "firebrick2")+
  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Urban population")
```

```{r, echo =FALSE}

joineddf %>%
  filter(urban_rural == "Rural") %>%
  ggplot(aes(x=Risky_Hydro, y = ..count..))+
  geom_bar(fill = "firebrick2")+
  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Rural population")
```

```{r, echo =FALSE}
#Distribution checks 
joineddf %>%
  filter(gender == "Male") %>%
  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
  geom_bar(fill = "firebrick2")+
  labs(x= "Perceived Risk from Nuclear Energy", y = "male population")
```

```{r, echo =FALSE}
#Distribution checks 
joineddf %>%
  filter(gender == "Female") %>%
  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
  geom_bar(fill = "firebrick2")+
  labs(x= "Perceived Risk from Nuclear Energy", y = "Female population")
```

>>>>

---
title: "demographicvariablesregression"

output:
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
  pdf_document:

@@

summary(joineddf)

@@

```{r}
library(dplyr)

demovars <- joineddf %>%
  select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion))

summary(demovars)
table(demovars$gender)

```{r}
library(dplyr)

demovars_frisk <- demovars %>%
  select(starts_with("Risky"), gender) %>%
  filter(gender == "Female")%>%
  na.omit()

demovars_mrisk <- demovars %>%
  select(starts_with("Risky"), gender) %>%
  filter(gender == "Male") %>%
  na.omit()

sum_frisk <- demovars_frisk %>% 
    summarise(across(starts_with("Risky"), list(mean = mean, sd = sd, median = median, n = nrow))) %>%
    pivot_longer(cols = starts_with("Risky"), 
                                          names_to = c("Risky", "Technology", "stat"), 
                                          names_sep =  "_",
                                          values_to = "Value")%>%
    select(-Risky) %>%
    pivot_wider(names_from = stat, values_from = Value)%>%
    mutate(gender = "f")

sum_mrisk <- demovars_mrisk %>% 
    summarise(across(starts_with("Risky"), list(mean = mean, sd = sd, median = median, n = nrow))) %>%
    pivot_longer(cols = starts_with("Risky"), 
                                          names_to = c("Risky", "Technology", "stat"), 
                                          names_sep =  "_",
                                          values_to = "Value")%>%

    select(-Risky) %>%
    pivot_wider(names_from = stat, values_from = Value)%>%
    mutate(gender = "m")

```{r}
library(ggplot2)

# Combine the two datasets
sum_gender <- rbind(sum_frisk, sum_mrisk)

# Plot

p1 <- sum_gender%>% 
  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p2 <- sum_gender%>% 
  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceived risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

library(gridExtra)
grid.arrange(p1, p2, ncol = 2)

```{r}

# conducting 
library(stats)

male_risk <- demovars[demovars$gender == "Male",]$Risky_Nuclear
female_risk <- demovars[demovars$gender == "Female",]$Risky_Nuclear

wilcox.test(male_risk, female_risk, alternative = "two.sided")

library(dplyr)
library(purrr)

demovars %>% 
  filter(gender %in% c("Male", "Female"))%>%
  select(starts_with("Risky")) %>% 
  lapply(function(col) wilcox.test(col ~ gender, data = demovars))
